Fusion Moves for Correlation Clustering

### 2014-11-14 paper/abstract-new.tex
fixed typo

Correlation clustering, or multicut partitioning,
is a widely used in image segmentation for
partitioning an undirected graph or image with positive and negative edge weights 
such that the sum of cut edge weights is minimized.
%
Due to its NP-hardness, exact solvers do not scale and approximative solvers often give nonsatisfying results.

>>>>

Correlation clustering, or multicut partitioning,
is widely used in image segmentation for
partitioning an undirected graph or image with positive and negative edge weights 
such that the sum of cut edge weights is minimized.
%
Due to its NP-hardness, exact solvers do not scale and approximative solvers often give nonsatisfying results.
